\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-04 paper/main.tex

\title[short Title]{\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction}
\author[Sample \textit{et~al}.]{Tilman Hinnerichs\,$^{\text{\sfb 1,}*}$ and Robert Hoehndorf\,$^{\text{\sfb 2}}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
$^{\text{\sf 2}}$Department, Institution, City, Post Code,
Country.}

@@

The update rule for each individual node is
\begin{equation}
	\mathbf{x}^{\prime}_i = \mathbf{\Theta} \sum^{N}_{j}
	\frac{1}{\sqrt{\hat{d}_j \hat{d}_i}} \mathbf{x}_j
\end{equation}
where both $\hat{d}_i, \hat{d}_j$ are dependent on the edge weights
$e_{ij}$ of the graph. With simple, single-valued edge weights such as
$e_{ij}=1 \text{ }\forall (i,j)\in E$, all $\hat{d}_i$ reduce to
$d_i$, i.e., the degree of each vertex $i$. We denote this type of
graph convolutional neural layers with \textsc{GCNConv}.

@@

@@

Within DTI prediction, there are potential biases resulting from the
underlying datasets \citep{Pahikkala2014}. First, novel drugs are
often designed by altering non-functional components of a drug,
leading to two and more very similar drugs designed to target the same
proteins \cite{Overington2006}. This can result in a bias when it
leads to hidden duplicates that can distribute among the train/test
split, resulting in a better (measured) predictive performance than
would be expected when the model is applied to identify drugs that
target a protein for which no drugs yet exist. Second, some proteins
(which we will denote as \textit{hub proteins}) have significantly
more known interactions with drugs than others. In the STITCH
database, $5\%$ of the proteins have $40\%$ of the interactions, and
similar distributions are present in the Yamanishi and Drugbank
datasets \cite{Drugbank2007, Drugbank2017} datasets; preferentially
predicting these proteins may increase predictive performance while
again not reflecting the actual performance when applied to a new
protein (e.g., a protein for which no interactions are known). These
differences in the number of drugs targeting certain proteins may be
the result of study bias where more ``valuable'' proteins have more
drugs designed to target them due to their involvement in more common
diseases (or diseases for which drugs can be more profitably
marketed).

We developed \name as a computational model to predict drug--target
interactions. Specifically, given a protein, \name will identify and
rank known drugs that likely target this protein. \name combines two
types of features: structural information for drugs and proteins that
can be used to determine if they may physically interact, and
information about drug effects that may localize on an interaction
network.  As structural features, \name uses structural
representations of drugs from the SMILES transformer
\cite{SmilesTransformer} and representations of protein amino acid
sequences from DeepGOPlus \cite{DeepGoPlus}.  \name learns
representations of drug effects and protein functions using the
ontology-based machine learning method DL2Vec \cite{DL2vec2020}.

\todo[inline]{Move to methods:}
When combining ontology and molecular features with or without the
graph model, we concatenate both protein features and both drugs
features, before plugging them into the graph or the similarity
computation.

We use two half-twin neural networks to combine the molecular and
phenotype representations of drugs and proteins, and add these to a
protein interaction network as node labels.  We then train this model
in an end-to-end manner using a graph neural network architecture.
The overall workflow\todo{make sure it's a workflow} is depicted in
Figure~\ref{fig:Fullmodel}.

@@

\begin{figure}[!tpb]
	\centerline{\includegraphics[width=0.45\textwidth]{figures/full_model.png}}
	\caption{Full DTI prediction model based on the pretrained learnable feature transformations (LFT) for either molecular structure or ontology based features. The transformed protein representations are added to each corresponded protein as node features for the graph convolutional steps. }
	\label{fig:Fullmodel}
\end{figure}

\begin{figure}[!tpb]
	\centerline{\begin{tabular}{|p{2.2cm}|p{0.9cm}|p{0.75cm}|p{0.9cm}|p{0.75cm}|}
		\hline
		STITCH results&\multicolumn{4}{c|}{PPI graph}\\
		&\multicolumn{2}{c|}{without}&\multicolumn{2}{c|}{with}\\
		&AUROC&Micro $AUC_p$&AUROC&Micro $AUC_p$\\
		\hline
		MolPred&$0.69$&$0.65$&$0.69$&$0.67$\\
		\hline
		OntoPred&$0.88$&$0.87$&$0.92$&$0.93$\\
		\hline
		MolPred + OntoPred & $0.89$ & $0.90$&$0.93$&$0.94$\\
		\hline
		\hline
		Yamanishi results&\multicolumn{4}{c|}{PPI graph}\\
		&\multicolumn{2}{c|}{without}&\multicolumn{2}{c|}{with}\\
		&AUROC&Micro AUC&AUROC&Micro $AUC_p$\\
		\hline
		MolPred + OntoPred & $0.83$ & $0.82$&$0.84$&$0.84$\\
		\hline
	\end{tabular}}
	\caption{Results for \name on STITCH and Yamanishi dataset evaluated with a 5-fold cross-validation. MolPred and OntoPred are the predictors for molecular and ontology based features, respectively. }
	\label{tab:STITCHresults}
\end{figure}

We first perform a cross-validation over proteins and validate our
results. Cross-validation over proteins aims to evaluate how the model
performs when tasked to identify drugs that may target a ``novel''
protein, i.e., one not seen during training.
\todo[inline]{Describe/add the CV results here.}

Second, we use the model trained on STITCH and evaluate the model on
the Yamanishi benchmark dataset\todo{This needs another sentence
  stating how you made sure there was no overlap in data.}.

\todo[inline]{Maybe remove microAUC here, introduce in next section?}
We trained, validated and finally tested all considered models on the
STITCH dataset using a 5-fold cross-validation over a protein
split; we then selected the best-performing models (with respect to
\textit{AUROC} and $MicroAUC_p$) and evaluate them on the Yamanishi
benchmark dataset. To evaluate the influence of the different
features separately, and determine whether they ``localize'' on the
PPI graph (and therefore can be exploited successfully by the graph
neural networks), we train and evaluate models with different types of
features, and with and without inclusion of the PPI graph,
separately.
Table \ref{tab:STITCHresults} shows the results.

\todo[inline]{Move to caption of table.}
We will hereby denote the molecular feature based predictor with
\textit{MolPred}, while abbreviating the ontology based, top-down
predictor with \textit{OntoPred}.

We find that the model using ontology-based features
(\textit{OntoPred}) is showing significantly\todo{significance test
  and p value? otherwise remove} better performance on STITCH compared
to using only molecular features. We also observe that only the model
using ontology-based features results in significantly\todo{p-val}
increased performance when incorporating the PPI graph.  This increase
can be observed with different graph neural network
architectures\todo{data not in the table}. While the {\em GCNConv} and
{\em GENConv} architecture already shows an improvement, the
\textit{ResGraphConv} blocks add a large amount of additional
learnable parameters to the network, leading to more expressive
power. To test whether the improvement is due to the number of
learnable parameters added or the result of better exploiting the
information about PPIs, we experiment with a graph model in which all
graph convolutional neural layers in the residual blocks are
removed\todo{is this still a graph model?}. This pruned network, with
no information on the protein--protein interactions, reached very
similarly results as the original \textit{OntoPred} model\todo{data
  not shown; and details missing from Methods} and showed no
improvement.

\todo[inline]{Not clear, need to reformulate:}
Furthermore, when substituting the original \textit{GENConv} layers with \textit{GCNConv} or other related layers in the graph convolutional step of the ResGraphConv blocks, this model would achieve once again no significant performance gain in comparison to the plain \textit{OntoPred} one. This performance increase was only noticeable for \textit{GENConv} layers. The discrepancy of \textit{GENConv} and \textit{GCNConv} may be founded in numerical stability and fading signals, as described in the introduction of both methods.

As the inclusion of graph information significantly\todo{p val}
increases performance, we conclude that information about protein
functions localizes on the graph while molecular features do not.

@@

% \subsection{Baseline model}
Furthermore, we hypothesize that some of the predictions made by our
model are the result of the biases in drug--target interaction
datasets. We design a ``na\"ive'' baseline model that predicts the
same list of proteins for each drugs based on the number of
known drug--target interactions for a protein. Formally, given lists
$D$ and $P$ of drugs and proteins and a set of known interactions
$\mathcal{I} := \{(d_i, p_i) \}$, we construct an interaction matrix
$M_{int}\in\{0,1\}^{|D|\times|P|}$ with
\begin{equation*}
	M_{ij} = \begin{cases}
		1 & \text{if } (d_i, p_j)\in \mathcal{I}\\
		0 & otherwise
	\end{cases}
\end{equation*}
describing for all drug--protein pairs whether there is a known
interaction or not. We now rank all proteins $p_j\in P$ descending by
their number of drug interactors by summing over the columns of
$M_{ij}$ and ranking these sums:
\begin{equation*}
	f: P \rightarrow \mathbb{N} \text{ with } f:p_j \mapsto \sum_{i=1}^{|D|}M_{ij}
\end{equation*}
Our ``na\"ive'' predictor $P_k$  predicts all drugs to interact with
the top $k$ targets
% , denoted by $Top_k(P)$ 
with respect to
% $M_{ij}$ from
the introduced ranking:
\begin{equation*}
	P_k: D\times P \rightarrow \{0,1\} \text{ with } P_k: d_i, p_j \mapsto \begin{cases}
		1 & \text{ if }p_j \in Top_{k}(P)\\
		0 & otherwise
	\end{cases}
\end{equation*}
with the only hyperparameter $k$.
The prediction $P_k$ is not dependent on the drug $d_i$ and will
predict the same ranked list of drugs for a given protein $p_j$;
consequently, this na\"ive predictor does not predict any useful
information about interactions between drugs and proteins.
% Also note the possibility for a similar predictor by calculating the top $k$ interacting drugs, respectively.

We apply this naive predictor on both the STITCH and Yamanishi
datasets, using the full dataset as well as 5-fold cross-validation
over drugs and drug--protein pairs.
% Note, that this baseline predictor is not applicable for a protein split CV, as the amount of interactions is unknown. 
For each fold, we gradually increase $k$, eventually saving the best
performance for each fold. Using the full dataset, drug--target split,
and drug split, we obtain \todo[inline]{merge table results in
  text}\todo{are these micro or macro AUC?}.

\centerline{\begin{tabular}{|l|p{1.5cm}|p{1.5cm}|p{1.5cm}|}
	\hline
	Dataset&\multicolumn{3}{c|}{Splitting scheme}\\
	&Whole&DT pairs&Drugs\\
	\hline
	STITCH& $0.76$& $0.70$ & $0.73$\\
	\hline
	Yamanishi& $0.88$& $0.84$&$0.85$\\ 
	\hline
\end{tabular}}

The baseline predictor shows significantly\todo{p-val} higher
performance than a random classifier on both datasets, with better
results on the Yamanishi benchmark.

For comparison with the state of the art methods, we chose the best
performing methods for drug--target interaction prediction that were
previously evaluated on the Yamanishi benchmark dataset. These
state-of-the-art methods approaches include  DTIGEMS+
\cite{DTIGEMS2020} and DTI-CDF \cite{DTI-CDF2019}, which have showed
superior results in comparison to numerous works. Furthermore, we
added DTINet \cite{DTINet2017} as method for comparison which has been
used to develop a number of methods such as NeoDTI \cite{NeoDTI2019}
with similar methodology.

We evaluate all models on their recommended splitting scheme choice,
hyperparameters and folds in cross-validation, measuring their
respective AUROC. We further evaluate each model by performing a
protein-wise cross-validation determining (macro) AUROC and
$MicroAUC_p$. For this evaluation we allow stratification for the
training process but not for the validation and testing phase as
real world applications of these models would have to deal with
imbalanced data.

\todo[inline]{Merge the tables; add \name model to table to allow
  DIRECT comparison:}
The results of the analysis are summarized in the upper part of Figure
\ref{tab:Results}.

@@

	\centerline{\begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
		\hline
		Approach&\multicolumn{2}{c|}{Original scheme}&\multicolumn{2}{c|}{Protein split}\\
		&Splitting scheme&AUROC score&AUROC score&Micro $AUC_p$\\
		\hline
		DTINet&DP pairs&$0.91$&$0.84$&$0.67$\\
		DTIGEMS+&DP pairs&$0.93$& $0.72$& $0.68$ \\
		DTI-CDF&Proteins&$0.86$&$0.85$&$0.79$\\
		\hline
		\hline
		Approach&\multicolumn{2}{c|}{Original scheme}&\multicolumn{2}{c|}{Protein split}\\
		&Splitting scheme&AUROC score&AUROC score&Micro $AUC_p$\\
		\hline
		DeepDTI&Drugs&$0.88$&$0.76$&$0.70$\\
		DeepDTA&DP pairs&$0.88$&$0.77$&$0.69$\\
		DeepConv-DTI&DP pairs&$0.88$&$0.76$&$0.73$\\
		MolTrans&DP pairs&$0.90$&$0.77$&$0.74$\\
		\hline
	\end{tabular}}
	\caption{Test}
	\label{tab:Results}
\end{figure}

>>>>

\title[short Title]{\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction}git
\author[Sample \textit{et~al}.]{Tilman Hinnerichs\,$^{\text{\sfb 1,}*}$ and Robert Hoehndorf\,$^{\text{\sfb 2}}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
$^{\text{\sf 2}}$Department, Institution, City, Post Code,
Country.}

@@

The update rule for each individual node is given by a message passing scheme formalized by
\begin{equation}
	\mathbf{x}^{\prime}_i = \mathbf{\Theta} \sum^{N}_{j}
	\frac{1}{\sqrt{\hat{d}_j \hat{d}_i}} \mathbf{x}_j
\end{equation}
where both $\hat{d}_i, \hat{d}_j$ are dependent on the edge weights
$e_{ij}$ of the graph. With simple, single-valued edge weights such as
$e_{ij}=1 \text{ }\forall (i,j)\in E$, all $\hat{d}_i$ reduce to
$d_i$, i.e., the degree of each vertex $i$. We denote this type of
graph convolutional neural layers with \textsc{GCNConv}.

@@

\subsubsection{title}
Combining half-twin and graph convolutional neural networks, we map all protein representations to the respective node features, initializing the graph convolutional update steps. The resulting representations are used for a similarity prediction similar to the models presented in figure ~\ref{fig:HalfTwinNetwork}.  
When combining ontology and molecular features with or without the
graph model, we concatenate both protein features and both drugs
features, before plugging them into the graph for the similarity
computation. A more in-depth image of the overall architecture, combining both feature types is depicted in figure ~\ref{fig:FullModelAllLayers}.

@@

\todo[inline]{Introduction}
Within DTI prediction, there are potential biases resulting from the
underlying datasets \citep{Pahikkala2014}. First, novel drugs are
often designed by altering non-functional components of a drug,
leading to two and more very similar drugs designed to target the same
proteins \cite{Overington2006}. This can result in a bias when it
leads to hidden duplicates that can distribute among the train/test
split, resulting in a better (measured) predictive performance than
would be expected when the model is applied to identify drugs that
target a protein for which no drugs yet exist. Second, some proteins
(which we call \textit{hub proteins}) have significantly more known
interactions with drugs than others. In the STITCH database, $5\%$ of
the proteins have $40\%$ of the interactions, and similar
distributions are present in the Yamanishi and Drugbank
\cite{Drugbank2007, Drugbank2017} datasets; preferentially predicting
these proteins may increase predictive performance while not
reflecting the actual performance when applied to a new protein (e.g.,
a protein for which no interactions are known). These differences in
the number of drugs targeting certain proteins may be the result of
study bias where more ``valuable'' proteins have more drugs designed
to target them due to their involvement in more common diseases (or
diseases for which drugs can be more profitably marketed).

We developed \name as a computational model to predict drug--target
interactions. Specifically, given a protein, \name will identify and
rank drugs that likely target this protein. \name combines two types
of features: structural information for drugs and proteins that can be
used to determine if the drug and protein physically interact, and
information about phenotypic effects of drugs and changes in protein
function that may ``localize'' on an interaction network (i.e.,
neighboring nodes will share some of these features or be
phenotypically similar).  As structural features, \name uses
structural representations of drugs from the SMILES transformer
\cite{SmilesTransformer} and representations of protein amino acid
sequences from DeepGOPlus \cite{DeepGoPlus}.  \name learns
representations of drug effects and protein functions using the
ontology-based machine learning method DL2Vec \cite{DL2vec2020} and
ontology-based annotations of drugs and proteins.

We construct a PPI graph with proteins as nodes and protein-protein interactions as edges, mapping the protein features to each target as node features. \name then propagates information among the PPI network utilizing graph convolutional steps, calculating the similarity of drug and protein representation, and thus eventually predicting whether there is an interaction. The full workflow scheme is depicted in figure~\ref{fig:ModelWorkflow}

@@

\begin{figure}[!tpb]
	\centering
	\includegraphics[width=0.9\columnwidth]{figures/model_workflow.png}
	\caption{Full DTI prediction model based on the pretrained
          learnable feature transformations (LFT) for either molecular
          structure or ontology based features. The transformed
          protein representations are added to each corresponded
          protein as node features for the graph convolutional
          steps.}
	\label{fig:ModelWorkflow}
\end{figure}

\begin{table}[!tpb]
	\begin{tabular}{|p{2.2cm}|p{0.9cm}|p{0.75cm}|p{0.9cm}|p{0.75cm}|}
		\hline
		STITCH results&\multicolumn{4}{c|}{PPI graph}\\
		&\multicolumn{2}{c|}{without}&\multicolumn{2}{c|}{with}\\
		&Macro AUC&Micro $AUC_p$&Macro AUC&Micro $AUC_p$\\
		\hline
		MolPred&$0.69$&$0.65$&$0.69$&$0.67$\\
		\hline
		OntoPred&$0.88$&$0.87$&$0.92$&$0.93$\\
		\hline
		MolPred + OntoPred & $0.89$ & $0.90$&$0.93$&$0.94$\\
		\hline
		\hline
		Yamanishi results&\multicolumn{4}{c|}{PPI graph}\\
		&\multicolumn{2}{c|}{without}&\multicolumn{2}{c|}{with}\\
		&Macro AUC&Micro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		MolPred + OntoPred & $0.83$ & $0.82$&$0.84$&$0.84$\\
		\hline
	\end{tabular} \medskip

	\begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
		\hline
		Approach&\multicolumn{2}{c|}{Original scheme}&\multicolumn{2}{c|}{Protein split}\\
		&Splitting scheme&Macro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		DTINet&DP pairs&$0.91$&$0.84$&$0.67$\\
		DTIGEMS+&DP pairs&$0.93$& $0.72$& $0.68$ \\
		DTI-CDF&Proteins&$0.86$&$0.85$&$0.79$\\
		\hline
		\hline
		Approach&\multicolumn{2}{c|}{Original scheme}&\multicolumn{2}{c|}{Protein split}\\
		&Splitting scheme&Macro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		DeepDTI&Drugs&$0.88$&$0.76$&$0.70$\\
		DeepDTA&DP pairs&$0.88$&$0.77$&$0.69$\\
		DeepConv-DTI&DP pairs&$0.88$&$0.76$&$0.73$\\
		MolTrans&DP pairs&$0.90$&$0.77$&$0.74$\\
		\hline
	\end{tabular}\\

	\caption{Results for \name on STITCH and Yamanishi dataset evaluated with a 5-fold cross-validation. MolPred and OntoPred are the predictors for molecular and ontology based features, respectively. We hereby denote the molecular feature based predictor with \textit{MolPred}, while abbreviating the ontology based, top-down predictor with \textit{OntoPred}.}
	\label{tab:STITCHresults}
\end{table}

We evaluate our model's ability to identify drug--target interactions
using different approaches and datasets. First, we perform a
cross-validation over proteins and validate our results. A
cross-validation over proteins aims to evaluate how the model performs
when tasked to identify drugs that may target a ``novel'' protein,
i.e., one not seen during training, or a protein for which a drug that
targets it should be predicted.

\todo[inline]{Describe/add the CV results here.}
\begin{itemize}
	\item 
\end{itemize}
We trained, validated and finally tested all considered models on the
STITCH dataset using a 5-fold cross-validation over a protein
split; we then selected the best-performing models (with respect to
\textit{AUROC/MacroAUC} and $MicroAUC_p$) and evaluate them on in 5-fold protein split cross validation on the Yamanishi benchmark dataset to avoid validation overfitting and yield more realistic testing results. To evaluate the influence of the different
features separately, and determine whether they ``localize'' on the
PPI graph (and therefore can be exploited successfully by the graph
neural networks), we train and evaluate models with different types of
features, and with and without inclusion of the PPI graph,
separately, comparing the molecular (MolPred) and phenotype based (OntoPred) predictor and a combination of both, concatenating both features.
Table \ref{tab:STITCHresults} shows the results of these experiments.

We find that the model using ontology-based features
(\textit{OntoPred}) is showing better performance on STITCH compared
to using only molecular features. We also observe that only the model
using ontology-based features results in
increased performance when incorporating the PPI graph. This increase
can be observed with different graph neural network
architectures and configurations. While the {\em GCNConv} and
{\em GENConv} architecture already shows some minor improvement, the
\textit{ResGraphConv} blocks add a large amount of additional
learnable parameters to the network, leading to more expressive
power. To test whether the improvement is due to the number of
learnable parameters added or the result of better exploiting the
information about PPIs, we experiment with a graph model in which all
graph convolutional neural layers in the residual blocks are
removed, resulting in a non--graph model. This pruned network, with
no information on the protein--protein interactions, reached very
similar results to the original \textit{OntoPred} model\todo{data
  not shown; and details missing from Methods} and showed no
improvement.

Furthermore, these major improvements are only provided by the \textit{GENConv} graph convolution scheme as part of the ResGraphConv blocks, as \textit{GCNConv} and other related graph convolutional methods fail to achieve any gain in comparison to the plain \textit{OntoPred} performance even when combined with the residual blocks. The discrepancy of {\em GENConv} and other graph convolutional methods may be founded in numerical stability and fading signals, as described in the introduction of the {\em GENConv} method.

As the inclusion of graph information increases performance, we conclude that information about protein
functions localizes on the graph while molecular features do not.

@@

% \subsection{Baseline model}
Furthermore, we hypothesize that some of the predictions made by our
model are the result of the biases in drug--target interaction
datasets. We design a ``na\"ive'' baseline model that predicts the
same list of proteins for each drugs based on the number of
known drug--target interactions for a protein. Formally, given lists
$D$ and $P$ of drugs and proteins and a set of known interactions
$\mathcal{I} := \{(d_i, p_i) \}$, we construct an interaction matrix
$M_{int}\in\{0,1\}^{|D|\times|P|}$ with
\begin{equation*}
	M_{ij} = \begin{cases}
		1 & \text{if } (d_i, p_j)\in \mathcal{I}\\
		0 & otherwise
	\end{cases}
\end{equation*}
describing for all drug--protein pairs whether there is a known
interaction or not. We now rank all proteins $p_j\in P$ descending by
their number of drug interactors by summing over the columns of
$M_{ij}$ and ranking these sums:
\begin{equation*}
	f: P \rightarrow \mathbb{N} \text{ with } f:p_j \mapsto \sum_{i=1}^{|D|}M_{ij}
\end{equation*}
Our ``na\"ive'' predictor $P_k$  predicts all drugs to interact with
the top $k$ targets
% , denoted by $Top_k(P)$ 
with respect to
% $M_{ij}$ from
the introduced ranking:
\begin{equation*}
	P_k: D\times P \rightarrow \{0,1\} \text{ with } P_k: d_i, p_j \mapsto \begin{cases}
		1 & \text{ if }p_j \in Top_{k}(P)\\
		0 & otherwise
	\end{cases}
\end{equation*}
with the only hyperparameter $k$.
The prediction $P_k$ is not dependent on the drug $d_i$ and will
predict the same ranked list of drugs for a given protein $p_j$;
consequently, this na\"ive predictor will not predict any useful
information about interactions between drugs and proteins, but allows
us to estimate the effect of potential biases in our evaluation
dataset.
% Also note the possibility for a similar predictor by calculating the top $k$ interacting drugs, respectively.

We apply this naive predictor on both the STITCH and Yamanishi
datasets, using the full dataset as well as 5-fold cross-validation
over drugs and drug--protein pairs.
Note, that this baseline predictor is not applicable for a protein split CV, as the number of interactions for each protein in the validation set is unknown. 
For each fold, we gradually increase $k$ to determine the best
performance for each fold. Using the full dataset, drug--target split,
and drug split, we obtain the following MacroAUC/AUROC score results. For STITCH database we obtain a performance of $0.76$ on the whole dataset, $0.70$ for the drug--target pairs and $0.73$ in case of the drug splitting scheme. While these results are fairly moderate, on Yamanishi dataset we yield MacroAUC scores of $0.88$, $0.84$ and $0.85$, for total dataset, DT pair split and drug split, respectively.

The na\"ive predictor shows great performance on Yamanishi dataset, with substantial gain in comparison to a random predictor on both datasets. In the following we will denote this nai\"ve predictor as a baseline predictor correlating its performance to state of the art models and \name.

For comparison with the state of the art methods, we chose the best
performing methods for drug--target interaction prediction that were
previously evaluated on the Yamanishi benchmark dataset. These methods include DTIGEMS+
\cite{DTIGEMS2020} and DTI-CDF \cite{DTI-CDF2019}, which have showed
superior results in comparison to numerous works. Furthermore, we
added DTINet \cite{DTINet2017} as method for comparison which has been
used to develop a number of methods such as NeoDTI \cite{NeoDTI2019}
with similar methodology.

We evaluate all models on their recommended splitting scheme choice,
hyperparameters and folds in cross-validation, measuring their
respective AUROC. We further evaluate each model by performing a
protein-wise cross-validation determining Macro AUC/AUROC score and
$MicroAUC_p$. For this evaluation we allow stratification for the
training process but not for the validation and testing phase as
real world applications of these models would have to deal with possibly
imbalanced data.

\todo[inline]{ add \name model to table to allow
  DIRECT comparison:}
The results of the analysis are summarized in the upper part of Figure
\ref{tab:Results}.

@@

	\centerline{}
	\caption{Test}
	\label{tab:Results}
\end{figure}
